OG-Analysis

### 2019-07-28 OG-Analysis.Rmd
Tested HC bulk and SEB

```{r read in data files}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean")
CD4<-dplyr::select(read.csv("OG_CD4_bulk_summary_clean.csv"), -X, -X.1)
CD4_OG<-dplyr::select(read.csv("OG_CD4_OG_summary_clean.csv"), -X, -X.1)
CD4_OG_TH1<-dplyr::select(read.csv("OG_CD4_OG.TH1_summary_clean.csv"), -X, -X.1)
CD4_OG_GT<-dplyr::select(read.csv("OG_CD4_OG.TH1_summary_clean.csv"), -X, -X.1)
CD4_OG_TNF<-dplyr::select(read.csv("OG_CD4_OG.TNFa_summary_clean.csv"), -X, -X.1)
PBMC<-dplyr::select(read.csv("DonorInfo_clean.csv"), -X)
    PBMC<-PBMC[grep("OG", PBMC$used),]
mimosa<-dplyr::select(read.csv("OG_MIMOSA_clean.csv"), -X)
    mimosa<-filter(mimosa, celltype=="CD4" & Exprate==0.01)
```

#pep
```{r pep total}
library(dplyr)
library(knitr)
DF<-subset(CD4, CD4$Stim=="WCL")
colnames<-names(numeric_only(DF))
for(col in colnames){
    y<-pvals_4_loose(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```

>>>>

```{r read in data files}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean")
CD4<-dplyr::select(read.csv("OG_CD4_bulk_summary_clean.csv"), -X, -X.1)
CD4_OG<-dplyr::select(read.csv("OG_CD4_OG_summary_clean.csv"), -X, -X.1)
CD4_OG_TH1<-dplyr::select(read.csv("OG_CD4_OG.TH1_summary_clean.csv"), -X, -X.1)
CD4_OG_GT<-dplyr::select(read.csv("OG_CD4_OG.TH1_summary_clean.csv"), -X, -X.1)
CD4_OG_TNF<-dplyr::select(read.csv("OG_CD4_OG.TNFa_summary_clean.csv"), -X, -X.1)
PBMC<-dplyr::select(read.csv("DonorInfo_clean.csv"), -X)
    PBMC<-PBMC[grep("OG", PBMC$used),]
mimosa<-dplyr::select(read.csv("OG_MIMOSA_clean.csv"), -X)
    mimosa<-dplyr::filter(mimosa, celltype=="CD4" & Exprate==0.01)
```

#HC
went through total cd4 un and seb --> no dif  
went through og cd4 seb --> no dif  
want the graph just in case

maybe this can go in a supp figure or something...  
went through og_GT seb and there are more tbet+gata3+ccr4+ cells  
went through og_TH1 seb and there are more tbet+gata3+ccr4+ cells  
went through og_TNF seb and there are more tbet+gata3+ccr4+ cells

```{r HC}
library(dplyr)
library(knitr)
DF<-mutate_hc(subset(CD4, CD4$Stim=="SEB"))
plot_hc(DF, "SM","OG_freq")
```

#pep
```{r pep total}
library(dplyr)
library(knitr)
DF<-subset(CD4, CD4$Stim=="PEP")
colnames<-numeric_only(DF)
for(col in colnames){
    y<-pvals_4_loose(DF, col)
    if(dim(y)[1]>0){
        print(col)
        print(y)}
}
```
